Geant4 Benchmark Analysis:\\ Al cube and He cylindrical chamber

### 2015-03-15 docs/Paper/paper.tex
Run and paper revision complete

Energy deposition signatures were acquired for protons and neutrons.  Figures \ref{fig:pEDep_eV} and \ref{fig:pEDep_keV} show a monotonically increaing function of energy deposition across the experimental distance $z$ for protons in the eV to keV range.  The MeV-range (fig~\ref{fig:pEDep_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.  The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}/2$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.  Up to 20 MeV, the total energy is deposited at $z=57.5 cm - L_{Al}/2$, after which the total deposition extends further in the $+z$ direction.  The last decade of energy probed exibits a dramatic increase in this extension, which increasingly exposes a gradual incline to a peak followed by a drop.

%% Proton EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
\label{fig:pEDep_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
\label{fig:pEDep_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
\label{fig:pEDep_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
\label{fig:nEDep_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
\label{fig:nEDep_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
\label{fig:nEDep_MeV}
\end{figurehere}
\vspace{0.2 cm}

Neutron energy deposition maps are found in figures \ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, and \ref{fig:nEDep_MeV}, following the same energy labeling schema.  The total energy deposition here also seems to monotonically increase until MeV-range energies, at which point the deposition sputters across various locations throughout the $57.5 cm \pm L_{Al}/2$ domain in $z$.  See Appendix~\ref{app:EDep} for energy deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.

@@

The average charge displacement per proton event is acquired and normalized by the gain equation (eqn.~\ref{eqn:gain}) in order to create a charge displacement landscapes.
\begin{equation}
  gain[z] = \frac{\sum \text{\emph{net charge @ $z$}} }{\sum \text{\emph{charge of primary particle}} } \label{eqn:gain}
\end{equation}
Up to around 10 keV proton energies (figs.~\ref{fig:pChargeDep_eV} and \ref{fig:pChargeDep_keV}) the nominal gain outside of the defined volumes (hence in air) are comparable to the magnitudes found between the boundaries of the Aluminum block.  Beyond 100 MeV proton energies (fig.~\ref{fig:pChargeDep_MeV}) a gain measurement may be found within the confines of the Helium cylinder, which exists within the range $z=100 cm \pm R_{He}$; for these figures, a large peak may be seen at the world's edge, $z=115 cm$.  The $-1e$ net gain at $z=0$ for all figures is where the collimated source originates.

No visible charge trasfer occurs with neutron primary events in the ev to keV energy range (figs.~\ref{fig:nChargeDep_eV} and \ref{fig:nChargeDep_keV}).  Only in MeV range beam energies (fig.~\ref{fig:nChargeDep_MeV}) do the neutron events charge transfer at the boundaries of both the Aluminum cube and Helium cylinder. See Appendix~\ref{app:ChargeDep} for charge deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.

%% Proton ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
\label{fig:pChargeDep_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
\label{fig:pChargeDep_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
\label{fig:pChargeDep_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
\label{fig:nChargeDep_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
\label{fig:nChargeDep_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
\label{fig:nChargeDep_MeV}
\end{figurehere}
\vspace{0.15 cm}

\subsection{Production Probabilities}

\section{Conclusions}

@@

\end{thebibliography}

\end{multicols}

\appendix
\newpage
\section{Energy deposition for Al side = 10, 25 cm}\label{app:EDep}

\newpage
\section{Charge deposition for Al side = 10, 25 cm}\label{app:ChargeDep}

\end{document}

>>>>

Energy deposition signatures were acquired for protons and neutrons.  Figures \ref{fig:pEDep_Al5_eV} and \ref{fig:pEDep_Al5_keV} show a monotonically increaing function of energy deposition across the experimental distance $z$ for protons in the eV to keV range.  The MeV-range (fig~\ref{fig:pEDep_Al5_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.  The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}/2$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.  Up to 20 MeV, the total energy is deposited at $z=57.5 cm - L_{Al}/2$, after which the total deposition extends further in the $+z$ direction.  The last decade of energy probed exibits a dramatic increase in this extension, which increasingly exposes a gradual incline to a peak followed by a drop.

%% Proton EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
\label{fig:pEDep_Al5_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
\label{fig:pEDep_Al5_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
\label{fig:pEDep_Al5_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
\label{fig:nEDep_Al5_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
\label{fig:nEDep_Al5_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
\label{fig:nEDep_Al5_MeV}
\end{figurehere}
\vspace{0.2 cm}

Neutron energy deposition maps are found in figures \ref{fig:nEDep_Al5_eV}, \ref{fig:nEDep_Al5_keV}, and \ref{fig:nEDep_Al5_MeV}, following the same energy labeling schema.  The total energy deposition here seems to monotonically increase indefinitely; upon reaching MeV-range energies, deposition distributes itself relatively evenly with a bias towards the right across the $57.5 cm \pm L_{Al}/2$ domain in $z$.  See Appendix~\ref{app:EDep} for energy deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.

@@

The average charge displacement per proton event is acquired and normalized by the gain equation (eqn.~\ref{eqn:gain}) in order to create a charge displacement landscapes.
\begin{equation}
  gain[z] = \frac{\sum \text{\emph{net charge @ z}} }{\sum \text{\emph{charge of primary particle}} } \label{eqn:gain}
\end{equation}
Up to around 10 keV proton energies (figs.~\ref{fig:pChargeDep_Al5_eV} and \ref{fig:pChargeDep_Al5_keV}) the nominal gain outside of the defined volumes (hence in air) are comparable to the magnitudes found between the boundaries of the Aluminum block.  Beyond 100 MeV proton energies (fig.~\ref{fig:pChargeDep_Al5_MeV}) a gain measurement may be found within the confines of the Helium cylinder, which exists within the range $z=100 cm \pm R_{He}$; for these figures, a large peak may be seen at the world's edge, $z=115 cm$.  The $-1e$ net gain at $z=0$ for all figures is where the collimated source originates.

No visible charge trasfer occurs with neutron primary events in the ev to keV energy range (figs.~\ref{fig:nChargeDep_Al5_eV} and \ref{fig:nChargeDep_Al5_keV}).  Only in MeV range beam energies (fig.~\ref{fig:nChargeDep_Al5_MeV}) do the neutron events charge transfer at the boundaries of both the Aluminum cube and Helium cylinder. See Appendix~\ref{app:ChargeDep} for charge deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.

%% Proton ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
\label{fig:pChargeDep_Al5_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
\label{fig:pChargeDep_Al5_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
\label{fig:pChargeDep_Al5_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
\label{fig:nChargeDep_Al5_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
\label{fig:nChargeDep_Al5_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
\label{fig:nChargeDep_Al5_MeV}
\end{figurehere}
\vspace{0.15 cm}

\end{multicols}
\newpage
\subsection{Production Tallies}

There are no protons, neutrons nor gammas produced under 30 MeV proton beam energy, at which the number of gammas created per proton gradually increases with energy.  The first run which produced \emph{any} proton-neutron combination in any of the geometric setups occured at 200 MeV.  Particles production tallies for protons at 500 MeV are shown in tables \ref{tab:production_pAl5}, \ref{tab:production_pAl10}, and \ref{tab:production_pAl25}.

\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=5 cm$} (unnormalized)}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.0732 & 0.0043 & 0.0009 & 0.0004 & 0 & 0 & 0 \\
    1 & 0.204 & 0.0453 & 0.0117 & 0.0082 & 0.005 & 0.0003 & 0.0024 \\
    2 & 0.1664 & 0.0493 & 0.0482 & 0.0138 & 0.0055 & 0.0028 & 0.0055 \\
    3 & 0.0888 & 0.0227 & 0.0324 & 0.0159 & 0.0071 & 0.0044 & 0.003 \\
    4 & 0.0476 & 0.0212 & 0.0259 & 0.021 & 0.0193 & 0.0127 & 0.0076 \\
    5 & 0.0221 & 0.0079 & 0.0073 & 0.0092 & 0.011 & 0.0068 & 0.0105 \\
    $>$5 & 0.0141 & 0.0065 & 0.0067 & 0.0067 & 0.0092 & 0.0074 & 0.0195 \\
    \hline\hline
  \end{tabular} \\
  \begin{tabular}{r} Gammas: 1.0737 \end{tabular}
  \label{tab:production_pAl5}
\end{centering}\end{tablehere}
\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=10 cm$}}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.0494 & 0.0045 & 0.0015 & 0.0001 & 0.0001 & 0.0001 & 0.0004 \\
    1 & 0.225 & 0.0462 & 0.0115 & 0.0078 & 0.0044 & 0.0022 & 0.0001 \\
    2 & 0.1848 & 0.0576 & 0.0534 & 0.0183 & 0.0098 & 0.0027 & 0.0012 \\
    3 & 0.0942 & 0.0215 & 0.0309 & 0.0218 & 0.0075 & 0.0058 & 0.0035 \\
    4 & 0.0557 & 0.0192 & 0.0264 & 0.0198 & 0.0231 & 0.0124 & 0.0154 \\
    5 & 0.0238 & 0.0067 & 0.0068 & 0.0073 & 0.0095 & 0.0074 & 0.0071 \\
    $>$5 & 0.0173 & 0.0094 & 0.0089 & 0.0089 & 0.0086 & 0.0087 & 0.018 \\
    \hline\hline
  \end{tabular} \\
  \begin{tabular}{r} Gammas: 1.0871 \end{tabular}  
  \label{tab:production_pAl10}
\end{centering}\end{tablehere}
\vspace{0.15 cm}
\begin{tablehere}\begin{centering}
  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=25 cm$}}
  \begin{tabular}{c || c c c c c c c}
    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
    \hline\hline
    0 & 1.0647 & 0.004 & 0.0008 & 0.0001 & 0.0001 & 0.0001 & 0.0007 \\
    1 & 0.2215 & 0.0452 & 0.0086 & 0.0047 & 0.0014 & 0.0004 & 0.0006 \\
    2 & 0.1781 & 0.0554 & 0.056 & 0.0156 & 0.0059 & 0.0022 & 0.0035 \\
    3 & 0.1063 & 0.0232 & 0.0289 & 0.019 & 0.007 & 0.005 & 0.0046 \\
    4 & 0.0591 & 0.023 & 0.0265 & 0.0242 & 0.0217 & 0.0127 & 0.0111 \\
    5 & 0.0255 & 0.0077 & 0.0086 & 0.0093 & 0.0065 & 0.0048 & 0.0078 \\
    $>$5 & 0.0178 & 0.0098 & 0.0094 & 0.0103 & 0.0109 & 0.0134 & 0.0224 \\
    \hline\hline
  \end{tabular} \\
  \begin{tabular}{r} Gammas: 1.1055 \\ \end{tabular}  
  \label{tab:production_pAl25}
\end{centering}\end{tablehere}
\vspace{0.15 cm}

\begin{multicols}{2}
\section{Conclusions}

High energy protons were necessary to penetrate the Aluminum cube and consequentially bring visibility to the Bragg curve, characterized by the stopping power of protons in each media due to pathway ionization.  The total energy deposited into the volumes curiously seems to decrease beyond the peak with respect to beam energy in figure \ref{fig:pEDep_Al5_MeV}; what occurs here is a complete transmission of proportionately many protons through the Aluminum cube, and a continued travel of the protons into the Helium chamber, seen by the demonstrative schematic (fig.~\ref{fig:schematic}).  This phenomena reappears in the charge deposition landscape of protons at high energies (fig.~\ref{fig:pChargeDep_Al5_MeV}), where we observe a conspicuous gain at the world's edge, $z=115cm$; the protons must then tramsmit directly through the Helium chamber to the edge of the defined world where the fine $z$-bin collects the charge of the primary.

Neutrons, which do not ionize their penetration pathways, do not behave with a Bragg curve but rather undergo elastic scattering and nuclear interactions.  The resulting destructive recoil effect is shown by the development of a energy deposition bias in the Aluminum cube (figs.~\ref{fig:nEDep_Al5_eV}, \ref{fig:nEDep_Al5_keV}, \ref{fig:nEDep_Al5_MeV}).  Relatively few high energy neutrons are also found to transmit directly through the cube, evidenced by the small shifts in charge deposiition (fig.~\ref{fig:nChargeDep_Al5_MeV}) due to obliterated electrons travelling but tens of microns.

@@

\end{thebibliography}
\end{multicols}
\appendix
\newpage
\section{Energy deposition for Al side of 10, 25 cm}\label{app:EDep}

%% Proton EDep figures
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
\label{fig:pEDep_Al10_eV}
\end{figurehere}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
\label{fig:pEDep_Al10_keV}
\end{figurehere}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
\label{fig:pEDep_Al10_MeV}
\end{figurehere}

%% Neutron EDep figures
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
\label{fig:nEDep_Al10_eV}
\end{figurehere}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
\label{fig:nEDep_Al10_keV}
\end{figurehere}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
\label{fig:nEDep_Al10_MeV}
\end{figurehere}

%% Proton EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
\label{fig:pEDep_Al25_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
\label{fig:pEDep_Al25_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
\label{fig:pEDep_Al25_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron EDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_eV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
\label{fig:nEDep_Al25_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_keV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
\label{fig:nEDep_Al25_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_MeV.png}}
\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
\label{fig:nEDep_Al25_MeV}
\end{figurehere}
\vspace{0.2 cm}

\end{multicols}
\newpage
\section{Charge deposition for Al side of 10, 25 cm}\label{app:ChargeDep}

%% Proton ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
\label{fig:pChargeDep_Al10_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
\label{fig:pChargeDep_Al10_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
\label{fig:pChargeDep_Al10_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
\label{fig:nChargeDep_Al10_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
\label{fig:nChargeDep_Al10_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
\label{fig:nChargeDep_Al10_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Proton ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
\label{fig:pChargeDep_Al25_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
\label{fig:pChargeDep_Al25_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
\label{fig:pChargeDep_Al25_MeV}
\end{figurehere}
\vspace{0.15 cm}

%% Neutron ChargeDep figures
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_eV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
\label{fig:nChargeDep_Al25_eV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_keV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
\label{fig:nChargeDep_Al25_keV}
\end{figurehere}
\vspace{0.15 cm}
\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_MeV.png}}
\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
\label{fig:nChargeDep_Al25_MeV}
\end{figurehere}
\vspace{0.15 cm}

\end{multicols}
\end{document}
